### 2009-11-11 doc/manuals/janitor/tex_installation/installation.tex
Interchange DEBUG and VERBOSE loglevels.

log4perl.appender.MainLog = Log::Log4perl::Appender::File
log4perl.appender.MainLog.Threshold = VERBOSE
log4perl.appender.MainLog.filename = /var/log/janitor.log
log4perl.appender.MainLog.layout = PatternLayout
log4perl.appender.MainLog.layout.ConversionPattern = %d %p> %m%n

>>>>

log4perl.appender.MainLog = Log::Log4perl::Appender::File
log4perl.appender.MainLog.Threshold = DEBUG
log4perl.appender.MainLog.filename = /var/log/janitor.log
log4perl.appender.MainLog.layout = PatternLayout
log4perl.appender.MainLog.layout.ConversionPattern = %d %p> %m%n

### 2009-11-11 doc/manuals/user_interface/ui-data.tex
Interchange DEBUG and VERBOSE loglevels.

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcls [options] $<$URL$>$}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
    Options:&&\\
    \texttt{-h} && short help\\
    \texttt{-v} && print version information\\
    \texttt{-d} & \textit{debuglevel} &debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
    \texttt{-l} &  & detailed listing\\
    \texttt{-L} &  & detailed listing including URLs from which file can 
    be downloaded\\
    \texttt{-m} && display all available metadata\\
    Arguments:&&\\
    \texttt{URL} && file or directory URL\\
\end{longtable}

@@

\texttt{arccp}\index{arccp}\index{commands:arccp} is a powerful
tool to copy files over the Grid. It is a part of the A-REX,
but can be used by the User Interface as well.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arccp [options] $<$source$>$ $<$destination$>$}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
    Options:&&\\
    \texttt{-h} && short help\\
    \texttt{-v} && print version information\\
    \texttt{-d} & \textit{debuglevel} &debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
    \texttt{-y} & \textit{cache\_path} & path to local cache (use to put file into cache)\\
    \texttt{-p} && use passive transfer (does not work if secure is on, default if secure is not requested)\\
    \texttt{-n} && do not try to force passive transfer\\
    \texttt{-i} && show progress indicator\\
    \texttt{-u} && use secure transfer (insecure by default)\\
    \texttt{-r} & \textit{recursion\_level} & operate recursively (if possible) up to specified level (0 - no recursion)\\
    \texttt{-R} & \textit{number} & how many times to retry transfer of every file before failing\\
    \texttt{-t} & \textit{time} & timeout in seconds (default 20)\\
    \texttt{-f} && if the destination is an indexing service and not the same as the source and the destination is already registered, then the copy is normally not done. However, if this option is specified the source is assumed to be a replica of the destination created in an uncontrolled way and the copy is done like in case of replication\\
    \texttt{-T} && do not transfer file, just register it - destination must be non-existing meta-url\\
    Arguments:&&\\
    \texttt{source} && source URL\\
    \texttt{destination} && destination URL\\
\end{longtable}

@@

The \texttt{arcrm}\index{arcrm}\index{commands:arcrm}
command allows users to erase files at any location specified by a
valid URL.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcrm [options] $<$source$>$}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
    Options:&&\\
    \texttt{-h} && short help\\
    \texttt{-v} && print version information\\
    \texttt{-d} & \textit{debuglevel} &debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
    \texttt{-c} & &continue with meta-data even if it failed to delete real file\\
    Arguments:&&\\
    \texttt{source} && source URL\\
\end{longtable}

@@

\index{arcacl}\index{commands:arcacl}This command retrieves or modifies
access control information associated with a stored object if service
supports GridSite GACL language~\cite{gacl} for access control.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcacl [options] get$|$put $<$URL$>$}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
    \texttt{-d, -debug} & \textit{debuglevel} &debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
    \texttt{-v} && print version information\\
    \texttt{-h} && short help\\
   Arguments:&&\\
    \texttt{get} &\textit{URL}& get Grid ACL for the object\\
    \texttt{put} &\textit{URL}& set Grid ACL for the object\\
    \texttt{URL} && object URL; curently only gsiftp and sse URLs are supported\\
\end{longtable}

>>>>

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcls [options] $<$URL$>$}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
    Options:&&\\
    \texttt{-h} && short help\\
    \texttt{-v} && print version information\\
    \texttt{-d} & \textit{debuglevel} &debug level is one of  FATAL, ERROR, WARNING, INFO, VERBOSE or DEBUG\\
    \texttt{-l} &  & detailed listing\\
    \texttt{-L} &  & detailed listing including URLs from which file can 
    be downloaded\\
    \texttt{-m} && display all available metadata\\
    Arguments:&&\\
    \texttt{URL} && file or directory URL\\
\end{longtable}

@@

\texttt{arccp}\index{arccp}\index{commands:arccp} is a powerful
tool to copy files over the Grid. It is a part of the A-REX,
but can be used by the User Interface as well.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arccp [options] $<$source$>$ $<$destination$>$}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
    Options:&&\\
    \texttt{-h} && short help\\
    \texttt{-v} && print version information\\
    \texttt{-d} & \textit{debuglevel} &debug level is one of  FATAL, ERROR, WARNING, INFO, VERBOSE or DEBUG\\
    \texttt{-y} & \textit{cache\_path} & path to local cache (use to put file into cache)\\
    \texttt{-p} && use passive transfer (does not work if secure is on, default if secure is not requested)\\
    \texttt{-n} && do not try to force passive transfer\\
    \texttt{-i} && show progress indicator\\
    \texttt{-u} && use secure transfer (insecure by default)\\
    \texttt{-r} & \textit{recursion\_level} & operate recursively (if possible) up to specified level (0 - no recursion)\\
    \texttt{-R} & \textit{number} & how many times to retry transfer of every file before failing\\
    \texttt{-t} & \textit{time} & timeout in seconds (default 20)\\
    \texttt{-f} && if the destination is an indexing service and not the same as the source and the destination is already registered, then the copy is normally not done. However, if this option is specified the source is assumed to be a replica of the destination created in an uncontrolled way and the copy is done like in case of replication\\
    \texttt{-T} && do not transfer file, just register it - destination must be non-existing meta-url\\
    Arguments:&&\\
    \texttt{source} && source URL\\
    \texttt{destination} && destination URL\\
\end{longtable}

@@

The \texttt{arcrm}\index{arcrm}\index{commands:arcrm}
command allows users to erase files at any location specified by a
valid URL.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcrm [options] $<$source$>$}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
    Options:&&\\
    \texttt{-h} && short help\\
    \texttt{-v} && print version information\\
    \texttt{-d} & \textit{debuglevel} &debug level is one of  FATAL, ERROR, WARNING, INFO, VERBOSE or DEBUG\\
    \texttt{-c} & &continue with meta-data even if it failed to delete real file\\
    Arguments:&&\\
    \texttt{source} && source URL\\
\end{longtable}

@@

\index{arcacl}\index{commands:arcacl}This command retrieves or modifies
access control information associated with a stored object if service
supports GridSite GACL language~\cite{gacl} for access control.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcacl [options] get$|$put $<$URL$>$}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
    \texttt{-d, -debug} & \textit{debuglevel} &debug level is one of  FATAL, ERROR, WARNING, INFO, VERBOSE or DEBUG\\
    \texttt{-v} && print version information\\
    \texttt{-h} && short help\\
   Arguments:&&\\
    \texttt{get} &\textit{URL}& get Grid ACL for the object\\
    \texttt{put} &\textit{URL}& set Grid ACL for the object\\
    \texttt{URL} && object URL; curently only gsiftp and sse URLs are supported\\
\end{longtable}
